General thermodynamic constraints on magic state conversions for quantum computation

### 2021-04-17 magic_paper.tex
Added sigma -> sigma\prime calulation. Surprisingly simpler than I thought, even led to some cleaning up in the first - and last - elbow condition in the stabilizer proof and appendices

\title{Thermodynamic constraints for magic states in quantum computation}

@@

The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of the output Lorenz curve point which is vertically aligned with the first elbow of the input Lorenz curve. 
Comparing these two points leads to the bound
\begin{equation}
	R(\epsilon, \epsilon') \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
\end{equation}
For the limiting case of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
\begin{equation}
	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
\end{equation}

Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
Using the max--thauma properties of super-additivity and vanishing at free states, we obtain
\begin{align}
	&\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \theta_{\rm{max}}(\ketbra{\rm{S}}) + \epsilon \theta_{\rm{max}}\left(\frac{1}{3}\id \right) = \nonumber\\
	&(1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
\end{align}
so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as
\begin{equation}
	R = \frac{1}{n} = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon.
\end{equation}

@@

Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. For a fixed stabilizer state $\sigma$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state. The transition occurs at $\epsilon = \epsilon_\star$ where
\begin{equation}\label{eq:noise_transition}
	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
\end{equation}
If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state. Specifically, there is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
\end{equation}
such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists. The transition value for the noise is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
\end{equation}
The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
\begin{equation*}
w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation*}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
Case $\rm{(C2)}$ corresponds to
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
	\end{cases}
\end{equation}
so the multiplicity in both cases is $3^n$.

@@

In each of the three scenarios, it is simple to check that the input state's first elbow has $x_0$ coordinate closer to $0$ compared to the output state, $x_0 \leq x_0'$ (see~\cref{app:first_elb_loc} for details). Therefore, we can use the first elbow constraint, as described in~\cref{app:elb_constraints}, leading to the following distillation bounds,
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq
	\begin{cases}
		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
	\end{cases}
\end{equation}
Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.

@@

>>>>

\title{General thermodynamic constraints on magic state conversions for quantum computation}

@@

The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs. 
Comparing these two points leads to the bound
\begin{equation}
	R(\epsilon, \epsilon') \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
\end{equation}
For the limiting case of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
\begin{equation}
	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
\end{equation}

Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
Using the max--thauma properties of super-additivity and vanishing at free states, we obtain
\begin{align}
	&\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \theta_{\rm{max}}(\ketbra{\rm{S}}) + \epsilon \theta_{\rm{max}}\left(\frac{1}{3}\id \right) = \nonumber\\
	&(1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
\end{align}
so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as \nick{CALCULATING THAUMA EXACTLY AT THE MOMENT}
\begin{equation}
	R = \frac{1}{n} = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon.
\end{equation}

@@

Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. For a fixed stabilizer state $\sigma$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state. The transition occurs at $\epsilon = \epsilon_\star$ where
\begin{equation}\label{eq:noise_transition}
	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
\end{equation}
If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state. Specifically, there is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
\end{equation}
such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists. The transition value for the noise is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-2^{\beta/\beta_\star}}.
\end{equation}
The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
\begin{equation*}
w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation*}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
Case $\rm{(C2)}$ corresponds to
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
	\end{cases}
\end{equation}
so the multiplicity in both cases is $3^n$.

@@

In each of the three scenarios, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the following distillation bounds,
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq
	\begin{cases}
		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
	\end{cases}
\end{equation}
Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.

@@

We find numerically that the bounds derived above from the ascending part of the curve generally perform better than when considering the region around the Lorenz curve peak.
Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation.
Numerically ranging through the entire curve will improve our bounds incrementally, to an extent that depends on the intricate Lorenz curve structure.

\subsection{Distillation bounds and energy dependencies}
The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect. However it is possible to adapt these bounds and put them in a more natural light.

For this, we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$. This output state must be some other stabilizer state and so has a positive Wigner function also. The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol. Therefore, we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$. For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
\begin{equation}
(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
\end{equation}
The condition for this is $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the ones for the input state~\cite{Renes_2016}.

If the physical system has Hamiltonian $H$, and can be experimentally cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic costs of any distillation protocol in terms of how the protocol transforms $\sigma$ to some other equilibrium state $\sigma'$. For example, if $\sigma'$ is close to the ground state \nick{fun fact: ground states correspond to $\beta \rightarrow \infty$ which makes both Lorenz curves look very rectangular - should we include this as an insight?} of the system, we then know that a great deal of entropy is dumped by the process. This allows us to parameterise our distillation bounds in a more insightful way.

We consider an arbitrary change in the Hamiltonian driving the system, $H\rightarrow H'$ such that $\sigma' = e^{-\beta H'}/\Z'$, so the energetic parameters contributing to the Lorenz curve of the output state $\rho'$ relative to $\sigma'$ will change. 
Specifically, the first elbow coordinates of the output Lorenz curve can now be expressed as
\begin{equation}\label{eq:transformed_first_elb_coords}
	(x'_0, L'_0) =
	\begin{cases}
		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F'(\beta))}, v(\epsilon')^{n'} \right), &\hspace{-7pt} \rm{(C1')}	\vspace{10pt}\\
		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F'(\beta))}, (3u(\epsilon'))^{n'} \right), &\hspace{-7pt} \rm{(C2')}
	\end{cases}
\end{equation}
where now Case $\rm{(C1')}$ applies when $\epsilon' \leq \epsilon'_\star(\beta'_\star)$ (which encompasses the case $E'_s = E'_{\rm{max}}$) and Case $\rm{(C2')}$ applies when $\epsilon' > \epsilon'_\star(\beta'_\star)$ (which encompasses the case $\beta \geq \beta'_\star$).
It is therefore now possible to get the scenario $\rm{(C1)} \rightarrow \rm{(C2')}$ if the two Hamiltonians $H,H'$ are sufficiently different.

Using the first elbow constraint again leads to the following distillation bounds,
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq
	\begin{cases}
		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F'(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F'(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F'(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F'(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
	\end{cases}
\end{equation}

### 2021-04-17 notes/notes.tex
Added sigma -> sigma\prime calulation. Surprisingly simpler than I thought, even led to some cleaning up in the first - and last - elbow condition in the stabilizer proof and appendices

@@

>>>>

\subsection{Strange state MSD in the unital fragment}\label{app:lc_compare}

Consider the Strange state MSD process in the unital fragment,
\begin{equation}\label{eq:su_conversion}
    \rho_{\rm{S}}(n', \epsilon, 0) \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(n', \epsilon', n-n').
\end{equation}
We denote input state indices without a prime and target state indices with a prime,
\begin{align}
    I(i,j,k=1) &= j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon), \\
    I'(i',j',k') &= k' + \left[ (j'-1) + \sum_{\ell=0}^{i'-1} m_{\ell}(n', \epsilon') \right]9^{n-n'}.
\end{align}

Pointwise Lorenz curve comparison requires $x_{I} = x_{I'}$, so the question is: 
\begin{center}
\emph{Given a triplet $(i',j',k')$, what is the tuple $(i,j)$ such that $I(i,j) = I'(i',j',k')$?}
\end{center}

According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(i, j)$, such that for a given $i' = 0,\dots,n'$,
\begin{equation}
	j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon) = \sum_{\ell=0}^{i'} m_{\ell}(n', \epsilon').
\end{equation}

As a basic example, consider the process 
\begin{equation}
\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
\end{equation}
We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
\begin{equation}
	L_{I(i,j)} \geq L'_{I'(0, 1, 81)}
\end{equation}
where the first multiplicity of the target state is $m_0 = 1$.
The multiplicities of the initial state are $(1, 384, 4096)$.

The challenge is to find $i,j$ such that $i(i,j) = i'(0,1,81)$.
\nick{By trial and error}, we find that $(i,j) = (1, 80)$.
Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
\begin{align*}
	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
	\begin{split}
	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
	\end{split}
\end{align*}
and then compare them.

@@

\subsection{First elbow location}
\label{app:first_elb_loc}
Consider a magic state interconversion in a stabilizer $\sigma$--fragment, as in~\cref{eq:stdist}, where we remind that $n \geq n'$ and we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.

Here, we show that $x_0 \leq x'_0$ for any of the three scenarios outlined in the proof of our main theorem in~\cref{sec:stab}.\\

$\rm{(C1)} \rightarrow \rm{(C1)}$.
We know from statistical physics that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
	\begin{align*}
		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'		
	\end{align*}

$\rm{(C2)} \rightarrow \rm{(C1)}$.
We now use the slightly altered inequality $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$ to proceed,
	\begin{align*}
		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
		&\leq \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
		&\leq \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
	\end{align*}

$\rm{(C2)} \rightarrow \rm{(C2)}$.
Similarly in this scenario,
	\begin{align*}
		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} \\
		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} = x_0'	
	\end{align*}
